The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-13 thesis/paper.tex
Changed Lehman source

%%Lehman's laws (!!!improve later)
Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}. The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.

@@

%Structure of the interview
The interview was conducted using a semi-structured approach \cite{robson2002real}. Structure to the interview was provided by organising it around the software evolution theories \cite{chapin2001types} \cite{lehman1980programs}. Investigative and open-ended questions related to each category and law were asked to provide a basis for comparison between the answers and our initial analysis. The interviewee was encouraged to speak freely, even if it required a change in direction or topic. This was allowed in order to fulfil our exploratory goal of the study.

@@

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short period of its lifetime. It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider these factors to be the remaining threats to construct validity.

@@

The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

>>>>

%Re-write this section... it's wrong
Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}. The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.

@@

%Structure of the interview
The interview was conducted using a semi-structured approach \cite{robson2002real}. Structure to the interview was provided by organising it around the software evolution theories \cite{chapin2001types, lehman90sview}. Investigative and open-ended questions related to each category and law were asked to provide a basis for comparison between the answers and our initial analysis. The interviewee was encouraged to speak freely, even if it required a change in direction or topic. This was allowed in order to fulfil our exploratory goal of the study.

@@

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman90sview}. Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short period of its lifetime. It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider these factors to be the remaining threats to construct validity.

@@

The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.
